\layerOne{Weekly Reports}
\setcounter{section}{14}
\layerTwo{2015}
\setcounter{subsection}{36}
\layerThree{7 Sep 2015 - 11 Sep 2015}
\begin{itemize}
\item Made browser tabs closeable
\item Init Requirements and Specifications in LaTeX
\item Added Panic button to GUI
\item Image loading: XML file now derived from IMG file name and path instead of storing
that information in the IMG file.
\item Division of BigIntegers fixed, Multiplication of negative Integers fixed
\end{itemize}
\layerThree{14 Sep 2015 - 18 Sep 2015}
\begin{itemize}
\item Tested and documented some git features.
\item Produced con
icts in git: Managed to resolve them finally. It was challenging. Further
testing required.
\item Tried to install safari. Waiting for Help desk. . .
\item Made the browser work again. Several fixes: Removed layouter, changed locking mechanism,
set to native browser
\end{itemize}
\layerThree{21 Sep 2015 - 25 Sep 2015}
\begin{itemize}
\item Used XMF to do exercises with metaclasses
\end{itemize}
\layerThree{ToDo}
\begin{itemize}
\item improve webpage
\item Specify FormClient
\item git commands in Eclipse
\item (nextWeek) MeMo language requirements
\item pw protected folder: \url{https://wincent.com/wiki/git_repository_access_control}
\item Snippets
\item look at/play with Kernel (Object/Class/Attribute)
\item Use Notepad++ with syntax highlighting for user defined languages: \url{http://weblogs.asp.net/jongalloway/creating-a-user-defined-language-in-notepad}
\item HTMLViewer.xmf: Are ".o", ".xip", ".xto", ".xtd", ".xtml" still in use?
Welcome.xmf: requestURL. . .
requirements
\end{itemize}
